Average solar wind and geomagnetic activity influence on the equatorial plasma mass density at geosynchronous orbit

### 2016-07-26 paper/paper.tex
Paper closer to reproducing Takahashi 2010

\begin{figure}[tp!]
  \centering
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF107-case1-t020-tf25-GOES6.eps}
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF107-case1-t025-tf30-GOES6.eps}
  \caption{$D_{st}$ events of Figure~\ref{HourlyAveragedDstEvents} separated by the average $F10.7$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
  \label{fig:F107BinnedDstEvents}
\end{figure}

@@

\begin{figure}[tp!]
  \centering
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF107-case24-t020-tf25-GOES6.eps}
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF107-case24-t025-tf30-GOES6.eps}
  \caption{$\rho_{eq}$ events of Figure~\ref{HourlyAveragedRhoEvents} separated by the average $F10.7$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
  \label{fig:F107Binned}
\end{figure}

>>>>

\begin{figure}[tp!]
  \centering
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF_{10.7}-case1-t020-tf25-GOES6.eps}
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF_{10.7}-case1-t025-tf30-GOES6.eps}
  \caption{$D_{st}$ events of Figure~\ref{HourlyAveragedDstEvents} separated by the average $F10.7$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
  \label{fig:F107BinnedDstEvents}
\end{figure}

@@

\begin{figure}[tp!]
  \centering
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF_{10.7}-case24-t020-tf25-GOES6.eps}
  \includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedF_{10.7}-case24-t025-tf30-GOES6.eps}
  \caption{$\rho_{eq}$ events of Figure~\ref{HourlyAveragedRhoEvents} separated by the average $F10.7$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
  \label{fig:F107Binned}
\end{figure}
